Report on the Fourth Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE4)

### 2016-10-05 WSSSPE3/report/registrants.tex

Alice Allen & Astrophysics Source Code Library\\
Gabrielle Allen & NCSA\\
Janine Aquino & UCAR/NCAR Earth Observing Laboratory\\
Steven Brandt & Louisiana State University\\
Jed Brown & CU Boulder\\
Matthias Bussonnier & UC Berkeley\\
Jeffrey Carver & University of Alabama\\
Emily Chen & NCSA\\
Sou Cheng Choi &  NORC at the University of Chicago \&  Illinois Institute of Technology\\
Nancy Collins & NCAR\\
Ethan Davis & UCAR Unidata\\
Davide DelVento & NCAR/CISL\\
Yuhan Ding & Illinois Institute of Technology\\
Tim Dunne & KnowInnovation \\
Ward Fisher & UCAR/Unidata\\
Sandra Gesing & University of Notre Dame\\
Josh Greenberg & Sloan Foundation\\
Dan Gunter & LBNL\\
Ted Habermann & The HDF Group\\
James Hetherington & University College London\\
Neil Chue Hong & Software Sustainability Institute\\
Elisabeth Huffer & Lingua Logica/NASA \\
Lorraine Hwang & UC Davis - CIG\\
Raymond Idaszak & RENCI; University of North Carolina at Chapel Hill\\
Elizabeth Jessup & University of Colorado Boulder\\
Nick Jones & New Zealand eScience Infrastructure (NeSI)\\
Daniel Katz & U Chicago \& Argonne\\
Iain Larmour & EPSRC (UK)\\
Frank Löffler & Louisiana State University\\
Suresh Marru & Indiana University\\
Ryan May & UCAR/Unidata\\
Abigail Cabunoc Mayes & Mozilla Foundation\\
Jeff McWhirter & Geode Systems\\
Constantinos Michailidis & Knowinnovation\\
Don Middleton & NCAR\\
Mark Miller & SDSC\\
Pate Motter & University of Colorado\\
Jaroslaw Nabrzyski & University of Notre Dame\\
Patrick Nichols & National Center for Atmospheric Research\\
Kyle Niemeyer & Oregon State University\\
Laura Owen & NCSA\\
Abani Patra & Univ at Buffalo\\
Grace Peng & National Center for Atmospheric Research\\
Birgit Penzenstadler & California State University Long Beach\\
Lindsay Powers & The HDF Group\\
Bernie Randles & UCLA\\
Erin Robinson & Foundation for Earth Science\\
Daniel Sellars & CANARIE Inc\\
Nikolay Simakov & SUNY University at Buffalo\\
Ian Taylor & Cardiff University\\
Ilian Todorov & Science \& Technology Facilities Council, UK\\
Benjamin Tovar & University of Notre Dame\\
Gregory Tucker & University of Colorado at Boulder\\
Matthew Turk & NCSA\\
Colin Venters & University of Huddersfield\\
Alexander Vyushkov & University of Notre Dame\\
Fraser Watson & National Solar Observatory\\
Nic Weber & University of Washington\\
Daniel Ziskin & NCAR - ACOM\\

>>>>

Alice Allen & Astrophysics Source Code Library\\
Gabrielle Allen & NCSA\\
Janine Aquino & UCAR/NCAR Earth Observing Laboratory\\
Steven Brandt & Louisiana State University\\
Jed Brown & CU Boulder\\
Matthias Bussonnier & UC Berkeley\\
Jeffrey Carver & University of Alabama\\
Emily Chen & NCSA\\
Sou-Cheng Choi &  NORC at the University of Chicago \&  Illinois Institute of Technology\\
Nancy Collins & NCAR\\
Ethan Davis & UCAR Unidata\\
Davide DelVento & NCAR/CISL\\
Yuhan Ding & Illinois Institute of Technology\\
Tim Dunne & KnowInnovation \\
Ward Fisher & UCAR/Unidata\\
Sandra Gesing & University of Notre Dame\\
Josh Greenberg & Sloan Foundation\\
Dan Gunter & LBNL\\
Ted Habermann & The HDF Group\\
James Hetherington & University College London\\
Neil Chue Hong & Software Sustainability Institute\\
Elisabeth Huffer & Lingua Logica/NASA \\
Lorraine Hwang & UC Davis - CIG\\
Raymond Idaszak & RENCI; University of North Carolina at Chapel Hill\\
Elizabeth Jessup & University of Colorado Boulder\\
Nick Jones & New Zealand eScience Infrastructure (NeSI)\\
Daniel Katz & U Chicago \& Argonne\\
Iain Larmour & EPSRC (UK)\\
Frank L\"offler & Louisiana State University\\
Suresh Marru & Indiana University\\
Ryan May & UCAR/Unidata\\
Abigail Cabunoc Mayes & Mozilla Foundation\\
Jeff McWhirter & Geode Systems\\
Constantinos Michailidis & Knowinnovation\\
Don Middleton & NCAR\\
Mark Miller & SDSC\\
Pate Motter & University of Colorado\\
Jaroslaw Nabrzyski & University of Notre Dame\\
Patrick Nichols & National Center for Atmospheric Research\\
Kyle Niemeyer & Oregon State University\\
Laura Owen & NCSA\\
Abani Patra & Univ at Buffalo\\
Grace Peng & National Center for Atmospheric Research\\
Birgit Penzenstadler & California State University Long Beach\\
Lindsay Powers & The HDF Group\\
Bernie Randles & UCLA\\
Erin Robinson & Foundation for Earth Science\\
Daniel Sellars & CANARIE Inc\\
Nikolay Simakov & SUNY University at Buffalo\\
Ian Taylor & Cardiff University\\
Ilian Todorov & Science \& Technology Facilities Council, UK\\
Benjamin Tovar & University of Notre Dame\\
Gregory Tucker & University of Colorado at Boulder\\
Matthew Turk & NCSA\\
Colin Venters & University of Huddersfield\\
Alexander Vyushkov & University of Notre Dame\\
Fraser Watson & National Solar Observatory\\
Nic Weber & University of Washington\\
Daniel Ziskin & NCAR - ACOM\\

### 2016-10-05 WSSSPE3/report/wg_appendix_eng_design.tex

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Engineering Design Group Discussion}
\label{sec:appendix_eng_design}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\subsection{Description of Opportunity, Challenges, and Obstacles}
The opportunity was identified to distill existing software engineering and
sustainability design knowledge into ``bite sized'' chunks for the Computational
Science and Engineering Community. In addition, two primary challenges were
identified:
\begin{itemize}
\item Mapping of the principles to best practices.
\item Demonstrating the return on investment of those best practices.
\end{itemize}

\subsection{Key Next Steps}

@@

\subsection{Key Milestones and Responsible Parties}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Engineering Design Group Discussion}
\label{sec:appendix_eng_design}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\subsubsection{Description of Opportunity, Challenges, and Obstacles}
The opportunity was identified to distill existing software engineering and
sustainability design knowledge into ``bite sized'' chunks for the Computational
Science and Engineering Community. In addition, two primary challenges were
identified:
\begin{itemize}
\item Mapping of the principles to best practices.
\item Demonstrating the return on investment of those best practices.
\end{itemize}

\subsubsection{Key Next Steps}

@@

\subsubsection{Key Milestones and Responsible Parties}

### 2016-10-05 WSSSPE3/report/wg_appendix_funding_spec_expert.tex
A few more changes that seem to make sense.
last change

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Funding Research Programmer Expertise Group Discussion}
\label{sec:appendix_funding_spec_expert}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

There is some question about the most effective duration and percentage of full
time for a programmer's work on a project. At least three months is necessary
for the programmer to read into the science (RSEs must not become so disengaged
from research that they do not have time to read a few papers -- this will result
in code which does not meet scientific needs), but too long could result in an
RSE losing their flexibility, becoming so engaged in one project that when that
project ends, they find it hard to transfer. For this reason, we also recommend
that 40 percent is ideal; two projects per developer, with some time for
training and infrastructure work. Having two developers per project seems to be ideal,
in the sense that software development is enhanced by two pairs of eyes.

@@

\subsection{Plan for Future Organization and Future Needs}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Funding Research Programmer Expertise Group Discussion}
\label{sec:appendix_funding_spec_expert}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

There is some question about the most effective duration and percentage of full
time for a programmer's work on a project. At least three months is necessary
for the programmer to read into the science (RSEs must not become so disengaged
from research that they do not have time to read a few papers -- this will result
in code which does not meet scientific needs), but too long could result in an
RSE losing their flexibility, becoming so engaged in one project that when that
project ends, they find it hard to transfer. For this reason, we recommend
that 40\% is ideal; two projects per developer, with some time for
training and infrastructure work. Having two developers per project seems to be ideal,
in the sense that software development is enhanced by two pairs of eyes.

@@

\subsubsection{Plan for Future Organization and Future Needs}

### 2016-10-05 WSSSPE3/report/wg_main_best_practices.tex

The creation of such a ``best practices'' document will build upon the range of
activities and topics discussed at WSSSPE3 and associated prior meetings. This
working group
will attempt to distill the emerging body of knowledge into this document. The
large number of articles from the NSF funded SI2 projects (SSE and SSI),
``lightning talks,'' ``white papers,'' and reports from different workshops have
created a large if somewhat diffuse source for this report.

@@

For additional information about the discussion, see
Appendix~\ref{sec:appendix_best_practices}.

\subsubsection{Plans}
%\todo{short text here - not bullets}
The creation of a document on best practices needs a large and diverse community
involved. The group has enlisted over ten contributors from the attendees at the
WSSSPE3 and those on the mailing list. The primary mechanism for developing this
document will be to examine and analyze the success of several well known
community scientific software and organizations supporting scientific software.
The group will attempt then to abstract general principles and best practices. Some of
the tools identified for such analysis are the general purpose PETSc toolkit for
linear system solution, NWChem for computational chemistry and the CIG
(Computational Infrastructure for Geodynamics) organization dedicated to
supporting an ensemble of related tools for the geodynamics community. The group also
established a timeline and a rough outline (see
Appendix~\ref{sec:appendix_best_practices}) for the report.

>>>>

The creation of such a ``best practices'' document will build upon the range of
activities and topics discussed at WSSSPE3 and associated prior meetings. This
working group
will attempt to distill the emerging body of knowledge into this document. The
large number of articles from the NSF-funded SI2 projects (SSE and SSI),
``lightning talks,'' ``white papers,'' and reports from different workshops have
created a large if somewhat diffuse source for this report.

@@

For additional information about the discussion, see
Section~\ref{sec:appendix_best_practices}.

\subsubsection{Plans}
%\todo{short text here - not bullets}
The creation of a document on best practices needs a large and diverse community
involved. The group has enlisted over ten contributors from the attendees at the
WSSSPE3 and those on the mailing list. The primary mechanism for developing this
document will be to examine and analyze the success of several well known
community scientific software and organizations supporting scientific software.
The group will attempt then to abstract general principles and best practices. Some of
the tools identified for such analysis are the general purpose PETSc toolkit for
linear system solution, NWChem for computational chemistry and the CIG
(Computational Infrastructure for Geodynamics) organization dedicated to
supporting an ensemble of related tools for the geodynamics community. The group also
established a timeline and a rough outline (see
Section~\ref{sec:appendix_best_practices}) for the report.

### 2016-10-05 WSSSPE3/report/wg_main_metrics.tex

The group discussion began by agreeing on the common purpose of creating a set
of guidance giving examples of specific metrics for the success of scientific
software in use, why they were chosen, what they are useful to measure, and any
challenges and pitfalls; then publish this as a white paper. The group discussed
many questions related to useful metrics for scientific software including
addressing if there is a common set of metrics that can be filtered in some way,
can metrics be fit into a common template, which metrics would be the most
useful for each stakeholder, which metrics are the most helpful and how would we
assess this, how are metrics monitored, and many more. A more complete bulleted
list of these questions can be found in Appendix~\ref{sec:appendix_metrics}. Next, a roadmap for how to
proceed was discussed, including creating a set of milestones and tasks. The idea
was put forth for the group to interact with the organizing committee of the
2016 NSF Software Infrastructure for Sustained Innovation (SI2) PI workshop in
order to send a software metrics survey to all SI2 and related awardees as a
targeted and relevant set of stakeholders. The five solicitations for software
elements released under the NSF SI2 program all included metrics as a required
component with submitters requested to include {\it ``a list of tangible
metrics, with end user involvement, to be used to measure the success of the
software element developed, \dots''}. These metrics are then reported as part of
annual reports to NSF by the projects. Although neither the proposal text
describing the metrics nor the reported metric results are publicly available,
there is reason to believe that the community will be willing to provide this
information through a survey mechanism. This survey would be created by one of
the student group members. Similarly, it was suggested that a software metrics
survey be sent to the UK SFTF (Software For The Future, led by the Engineering
and Physical Sciences Research Council) and TRDF (Tools and Resources
Development Fund, led by the Biotechnology and Biological Sciences Research
Council) software projects to ask them what metrics would be useful to report.
The remainder of the discussion focused mainly on the creation of a white paper
on this topic. This resulted in a paper outline and writing assignments with the
goal of publishing in venues including WSSSPE4, IEEE CiSE (Institute of
Electrical and Electronic Engineers Computing in Science and Engineering
magazine), or JORS (Journal of Open Research Software). More information about
the group discussion is available in Appendix~\ref{sec:appendix_metrics}.

>>>>

The group discussion began by agreeing on the common purpose of creating a set
of guidance giving examples of specific metrics for the success of scientific
software in use, why they were chosen, what they are useful to measure, and any
challenges and pitfalls; then publish this as a white paper. The group discussed
many questions related to useful metrics for scientific software including
addressing if there is a common set of metrics that can be filtered in some way,
can metrics be fit into a common template, which metrics would be the most
useful for each stakeholder, which metrics are the most helpful and how would we
assess this, how are metrics monitored, and many more. A more complete bulleted
list of these questions can be found in Section~\ref{sec:appendix_metrics}. Next, a roadmap for how to
proceed was discussed, including creating a set of milestones and tasks. The idea
was put forth for the group to interact with the organizing committee of the
2016 NSF Software Infrastructure for Sustained Innovation (SI2) PI workshop in
order to send a software metrics survey to all SI2 and related awardees as a
targeted and relevant set of stakeholders. The five solicitations for software
elements released under the NSF SI2 program all included metrics as a required
component with submitters requested to include {\it ``a list of tangible
metrics, with end user involvement, to be used to measure the success of the
software element developed, \dots''}. These metrics are then reported as part of
annual reports to NSF by the projects. Although neither the proposal text
describing the metrics nor the reported metric results are publicly available,
there is reason to believe that the community will be willing to provide this
information through a survey mechanism. This survey would be created by one of
the student group members. Similarly, it was suggested that a software metrics
survey be sent to the UK SFTF (Software For The Future, led by the Engineering
and Physical Sciences Research Council) and TRDF (Tools and Resources
Development Fund, led by the Biotechnology and Biological Sciences Research
Council) software projects to ask them what metrics would be useful to report.
The remainder of the discussion focused mainly on the creation of a white paper
on this topic. This resulted in a paper outline and writing assignments with the
goal of publishing in venues including WSSSPE4, IEEE CiSE (Institute of
Electrical and Electronic Engineers Computing in Science and Engineering
magazine), or JORS (Journal of Open Research Software). More information about
the group discussion is available in Section~\ref{sec:appendix_metrics}.

### 2016-10-05 WSSSPE3/report/wg_main_publishing_SW.tex
changing subsections of 5 to not be first person

See Appendix~\ref{sec:appendix_publishing_SW} for more details about the
discussion.

@@

The plan is to create and curate a web page describing executable papers, their value, and
a list of what publishers support them. We expect the page to be available in
early January of 2016 on the Software Sustainability Institute's website.

>>>>

See Section~\ref{sec:appendix_publishing_SW} for more details about the
discussion.

@@

The plan is to create and curate a web page describing executable papers, their value, and
a list of what publishers support them. The group expects the page to be available in
early January of 2016 on the Software Sustainability Institute's website.

### 2016-10-05 WSSSPE3/report/wg_main_software_credit.tex

A number of groups external to WSSSPE (although with some overlapping members)
are also focused on aspects of software credit, including the FORCE11 Software
Citation Working Group (see plans for coordination below). In addition, a
Software Credit workshop\footnote{London Software Credit workshop:
\url{http://www.software.ac.uk/software-credit}} convened in London on October
19, following the conclusion of WSSSPE3. See
Appendix~\ref{sec:appendix_SW_credit} for more detailed discussion of related
activities.

@@

The majority of the remaining discussion focused on standardizing (1) the
metadata necessary for software to be cited and (2) the mechanism for citing
software in publications. Moreover, discussions also oriented around the
indexing of software citations necessary for establishing a software citation
network either integrated with the existing paper citation ecosystem or
complementary to it. See Appendix~\ref{sec:appendix_SW_credit} for a more
detailed summary of the working group's discussion on these topics.

>>>>

A number of groups external to WSSSPE (although with some overlapping members)
are also focused on aspects of software credit, including the FORCE11 Software
Citation Working Group (see plans for coordination below). In addition, a
Software Credit workshop\footnote{London Software Credit workshop:
\url{http://www.software.ac.uk/software-credit}} convened in London on October
19, following the conclusion of WSSSPE3. See
Section~\ref{sec:appendix_SW_credit} for more detailed discussion of related
activities.

@@

The majority of the remaining discussion focused on standardizing (1) the
metadata necessary for software to be cited and (2) the mechanism for citing
software in publications. Moreover, discussions also oriented around the
indexing of software citations necessary for establishing a software citation
network either integrated with the existing paper citation ecosystem or
complementary to it. See Section~\ref{sec:appendix_SW_credit} for a more
detailed summary of the working group's discussion on these topics.

### 2016-10-05 WSSSPE4_proposal/WSSSPE4_proposal.tex

Awarded funding is expected to be reimbursement of allowable expenses (travel, lodging, sustenance) of up to \$1,500 for participants traveling from outside Europe to the UK, up to \$1,000 for participants traveling from Europe outside the UK to the UK, and up to \$500 for participants traveling from within the UK.

@@

In our final report, we will discuss the demographics of the supported attendees, the compete set of workshop attendees, speakers, breakout group leads, and the leaders of activities that grow out the workshop. In all cases, while our ideal would be to have these demographics match the US or global population averages, our goal will be to significantly improve over academic STEM and tech industry norms.

@@

\item {\bf Participant Support: } \$41,500
{\it Funds are requested to partially support travel for 25 participants and presenters (at \$1,500 per participant) from US institutions across the country from the US to Manchester, UK, and 3 participants/presenters (at \$1,000 each)  from US institutions who are already in Europe to travel to Manchester, and 2 participants/presenters  (at \$500 each)  from US institutions who are already in the UK to travel to Manchester. Reimbursable costs include airfare, hotel, and sustenance.}

>>>>

Awarded funding is expected to be reimbursement of allowable expenses (travel, lodging, sustenance) of up to \$1,500 for participants traveling from outside Europe to the UK, up to \$1,000 for participants traveling from Europe outside the UK to the UK, and up to \$500 for participants traveling from within the UK.
We plan to support the travel of \textbf{at least 10 students}, which comprises \$15,000 of the overall request.

@@

In our final report, we will discuss the demographics of the supported attendees, the compete set of workshop attendees, speakers, breakout group leads, and the leaders of activities that grow out the workshop. In all cases, while our ideal would be to have these demographics match the US or global population averages, our goal will be to significantly improve over academic STEM and tech industry norms.
In addition, our goal is to support the travel of at least 10 students.

@@

\item {\bf Participant Support: } \$41,500
{\it Funds are requested to partially support travel for 25 participants and presenters (at \$1,500 per participant) from US institutions across the country from the US to Manchester, UK, and 3 participants/presenters (at \$1,000 each)  from US institutions who are already in Europe to travel to Manchester, and 2 participants/presenters  (at \$500 each)  from US institutions who are already in the UK to travel to Manchester. Reimbursable costs include airfare, hotel, and sustenance.
Out of the 25 participants, 10 positions will be reserved for students.}

### 2016-10-05 WSSSPE4_report/awardees.tex

Alice Allen & Astrophysics Source Code Library \\
Wolfgang Bangerth & Colorado State University, USA \\
Roman Bauer & Newcastle University, UK \\
Steven Brandt & Louisiana State University, USA \\
Emily Chen & University of Illinois Urbana-Champaign, USA \\
Bruce Childers & University of Pittsburgh, USA \\
Michael R.~Crusoe & Common Workflow Language Project \\
Stephan Druskat & Humboldt-Universit\"{a}t zu Berlin, Germany \\
Anshu Dubey & Argonne National Laboratory, USA \\
Iain Emsley & Oxford University, UK \\
Christopher Gwilliams & Cardiff University, UK \\
Lorraine Hwang & University of California Davis, USA \\
Ray Idaszak & RENCI, University of North Carolina at Chapel Hill, USA \\
Xinlian Liu & Hood College, USA \\
Frank Löffler & Louisiana State University, USA \\
Tengyu Ma & Vanderbilt University, USA \\
Robert H.~McDonald & Indiana University, USA \\
Jonah Miller & Perimeter Institute, Canada \\
Daniel Mosse & University of Pittsburgh, USA \\
Kyle E.~Niemeyer & Oregon State University, USA \\
Santiago N\'{u}\~{n}ez-Corrales & University of Illinois Urbana-Champaign, USA \\
Dominic Orchard & University of Kent, UK \\
Francisco Queiroz & Pontifical Catholic University of Rio de Janeiro, Brazil \\
Jean Salac & University of Virginia, USA \\
Janos Sallai & Vanderbilt University, USA \\
Eric Seidel & University of California San Diego, USA \\
Prabhjyot Singh Saluja & Southwest Oklahoma State University, USA \\
Karan Shah & Georgia Institute of Technology, USA \\
Sameer Shende & University of Oregon, USA

>>>>

Alice Allen & Astrophysics Source Code Library \\
Wolfgang Bangerth & Colorado State University, USA \\
Roman Bauer\textsuperscript{\textdagger} & Newcastle University, UK \\
Steven Brandt & Louisiana State University, USA \\
Emily Chen\textsuperscript{*} & University of Illinois Urbana-Champaign, USA \\
Bruce Childers & University of Pittsburgh, USA \\
Michael R.~Crusoe\textsuperscript{\textdagger} & Common Workflow Language Project \\
Stephan Druskat\textsuperscript{\textdagger} & Humboldt-Universit\"{a}t zu Berlin, Germany \\
Anshu Dubey & Argonne National Laboratory, USA \\
Iain Emsley\textsuperscript{*} & Oxford University, UK \\
Christopher Gwilliams\textsuperscript{\textdagger} & Cardiff University, UK \\
Lorraine Hwang & University of California Davis, USA \\
Ray Idaszak & RENCI, University of North Carolina at Chapel Hill, USA \\
Xinlian Liu & Hood College, USA \\
Frank Löffler & Louisiana State University, USA \\
Tengyu Ma\textsuperscript{*} & Vanderbilt University, USA \\
Robert H.~McDonald & Indiana University, USA \\
Jonah Miller\textsuperscript{*} & Perimeter Institute, Canada \\
Daniel Mosse & University of Pittsburgh, USA \\
Kyle E.~Niemeyer\textsuperscript{\textdagger} & Oregon State University, USA \\
Santiago N\'{u}\~{n}ez-Corrales\textsuperscript{*} & University of Illinois Urbana-Champaign, USA \\
Dominic Orchard & University of Kent, UK \\
Francisco Queiroz\textsuperscript{*} & Pontifical Catholic University of Rio de Janeiro, Brazil \\
Jean Salac\textsuperscript{*} & University of Virginia, USA \\
Janos Sallai & Vanderbilt University, USA \\
Prabhjyot (Singh) Saluja\textsuperscript{*} & Southwest Oklahoma State University, USA \\
Eric Seidel\textsuperscript{*} & University of California San Diego, USA \\
Karan Shah\textsuperscript{*} & Georgia Institute of Technology, USA \\
Sameer Shende & University of Oregon, USA

### 2016-10-05 WSSSPE4_report/wg_open_research_index.tex

>>>>

\note{Dan to write this}

Introduction to group here, including the overall objective of work in this area.

\subsubsection{Participants}

members of the working group

\subsubsection{Working group objective}

Specific things the working group wants to accomplish in the context of the larger objective.

\subsubsection{Gap or challenge}

What is the gap or challenge being addressed?

\subsubsection{Relevant people and resources}

What people, groups, or resources are needed.

\subsubsection{Plans}

What tasks will the working group undertake

\subsubsection{SMART steps}

What are the first SMART steps proposed?

\subsubsection{More information \& joining instructions}

How could a reader get more information or get more involved?
